### 2016-10-03 Supplemental.tex
update edits DB2

\section*{Supplemental Materials and Methods}
\subsection*{EMT model network architecture.} TGF$\beta$ is a major inducer of EMT in development, fibrosis, and carcinogenesis with different isoforms mediating various effects depending on specific cellular context \cite{Nawshad:2005pi}.
TGF$\beta$1 was first described as an inducer of EMT in normal mammary epithelial cells \cite{Miettinen1994} and has since been shown to mediate EMT in vitro in a number of different epithelial cells, including renal proximal tubular, DLD1 colon carcinoma, and most recently alveolar epithelial cells \cite{Fan1999, Hales1994,Kasai2005,Willis2005}.
TGF$\beta$ signaling occurs through the Smad pathway in which signals are transduced by transmembrane serine/threonine kinase type I (ALK5) and type II (TGF$\beta$RII) receptors.
To increase ligand affinity, betaglycan (TGF$\beta$RIII) can also interact with TGF$\beta$RI,II \cite{Gatza:2010if}.
Upon TGF$\beta$ stimulation, the receptors are internalized into early endosomes where Smad anchor for receptor activation (SARA) modulates formation of complexes with (R-Smad) Smad2 or Smad3.
Smad2 and Smad3 are then phosphorylated at serine residues by the type I receptor \cite{Massague:2005qc}.
Phosphorylation induces their association with (Co-Smad) Smad4 and translocation to the nucleus where they interact with other transcription factors to regulate the transcription of TGF$\beta$ responsive genes, including alpha-smooth muscle actin, collagen1A2, vimentin, fibronectin, and plasminogen activator inhibitor-1 (PAI-1) by interacting with Smad-binding elements \cite{Dennler:2002hl,Derynck:2003fc}.
To regulate TGF$\beta$ signaling, Smurf2 (a ubiquitin E3 ligase) can become activated to mediate proteasome dependent degradation of Smad2 or bind with Smad 7 to target TGF$\beta$ receptor for degradation \cite{Kavsak2000,Bonni2001}.

@@

\begin{figure}
\includegraphics [width=1.0\linewidth] {./figs/Fig-5-Supplemental-ErrorTable.pdf}
\caption{Training and prediction values for the 11 TGF-$\beta$ objective functions versus a random parameter control.}\label{fig:S5}
\end{figure}

@@

%\bibliography{References_v1}

>>>>

\documentclass[12pt]{article}
% Load packages
\usepackage{url}  % Formatting web addresses
\usepackage{ifthen}  % Conditional
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{graphicx}
\usepackage[margin=0.1pt,font=footnotesize,labelfont=bf]{caption}
\usepackage{setspace}
%\usepackage{longtable}
\usepackage{colortbl}
%\usepackage{palatino,lettrine}
%\usepackage{times}
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\usepackage[wide]{sidecap}
\usepackage[authoryear,round,comma,sort&compress]{natbib}
\usepackage[authoryear,round]{natbib}
\usepackage{supertabular}
\usepackage{simplemargins}
\usepackage{lineno}

\urlstyle{rm}

%\textwidth = 6.50 in
%\textheight = 9.5 in
%\oddsidemargin =  0.0 in
%\evensidemargin = 0.0 in
%\topmargin = -0.50 in
%\headheight = 0.0 in
%\headsep = 0.25 in
%\parskip = 0.15in
%\linespread{1.75}
\doublespace

\setallmargins{1in}

%\bibliographystyle{plain}
\bibliographystyle{msb}

\makeatletter
\renewcommand\subsection{\@startsection
	{subsection}{2}{0mm}
	{-0.05in}
	{-0.5\baselineskip}
	{\normalfont\normalsize\bfseries}}
\renewcommand\subsubsection{\@startsection
	{subsubsection}{2}{0mm}
	{-0.05in}
	{-0.5\baselineskip}
	{\normalfont\normalsize\itshape}}
\renewcommand\section{\@startsection
	{subsection}{2}{0mm}
	{-0.2in}
	{0.05\baselineskip}
	{\normalfont\large\bfseries}}
\renewcommand\paragraph{\@startsection
	{paragraph}{2}{0mm}
	{-0.05in}
	{-0.5\baselineskip}
	{\normalfont\normalsize\itshape}}
\makeatother

%Review style settings
%\newenvironment{bmcformat}{\begin{raggedright}\baselineskip20pt\sloppy\setboolean{publ}{false}}{\end{raggedright}\baselineskip20pt\sloppy}

%Publication style settings

% Single space'd bib -
\setlength\bibsep{0pt}

\renewcommand{\rmdefault}{phv}\renewcommand{\sfdefault}{phv}

% Change the number format in the ref list -
\renewcommand{\bibnumfmt}[1]{#1.}

% Change Figure to Fig.
\renewcommand{\figurename}{Fig.}

\begin{document}
\section*{Supplemental Materials and Methods}
\subsection*{EMT model network architecture.} TGF$\beta$ is a major inducer of EMT in development, fibrosis, and carcinogenesis with different isoforms mediating various effects depending on specific cellular context \cite{Nawshad:2005pi}.
TGF$\beta$1 was first described as an inducer of EMT in normal mammary epithelial cells \cite{Miettinen1994} and has since been shown to mediate EMT in vitro in a number of different epithelial cells, including renal proximal tubular, DLD1 colon carcinoma, and most recently alveolar epithelial cells \cite{Fan1999, Hales1994,Kasai2005,Willis2005}.
TGF$\beta$ signaling occurs through the Smad pathway in which signals are transduced by transmembrane serine/threonine kinase type I (ALK5) and type II (TGF$\beta$RII) receptors.
To increase ligand affinity, betaglycan (TGF$\beta$RIII) can also interact with TGF$\beta$RI,II \cite{Gatza:2010if}.
Upon TGF$\beta$ stimulation, the receptors are internalized into early endosomes where Smad anchor for receptor activation (SARA) modulates formation of complexes with (R-Smad) Smad2 or Smad3.
Smad2 and Smad3 are then phosphorylated at serine residues by the type I receptor \cite{Massague:2005qc}.
Phosphorylation induces their association with (Co-Smad) Smad4 and translocation to the nucleus where they interact with other transcription factors to regulate the transcription of TGF$\beta$ responsive genes, including alpha-smooth muscle actin, collagen1A2, vimentin, fibronectin, and plasminogen activator inhibitor-1 (PAI-1) by interacting with Smad-binding elements \cite{Dennler:2002hl,Derynck:2003fc}.
To regulate TGF$\beta$ signaling, Smurf2 (a ubiquitin E3 ligase) can become activated to mediate proteasome dependent degradation of Smad2 or bind with Smad 7 to target TGF$\beta$ receptor for degradation \cite{Kavsak2000,Bonni2001}.

@@

\begin{figure}
\includegraphics [width=1.0\linewidth] {./figs/FigSX_error_table.pdf}
\caption{Training and prediction values for the 11 TGF-$\beta$ objective functions versus a random parameter control.}\label{fig:SX}
\end{figure}

\begin{figure}
\includegraphics [width=1.0\linewidth] {./figs/FigSX2_Handfit_VEGFA.pdf}
\caption{VEGF-A qPCR data used to hand fit VEGF enhancement of E-cadherin expression. mRNA was harvested after 3hr and 24hr timepoint.}\label{fig:SX2}
\end{figure}

@@

\bibliography{References_v1}

\end{document}
